The \dealii Library, Version 9.5

### 2023-07-07 9.5/paper.tex
List Stefano's acknowledgments. Plus a couple of edits.

\dealii's CMake project configuration itself now exports three targets,
\texttt{dealii::dealii\_debug}, \texttt{dealii::dealii\_release}, and
\texttt{dealii::dealii}. Linking against one of the first two variants via
\texttt{target\_link\_libraries()} populates the target with all necessary
include directories and the full link interface necessary for \dealii. The
third variant, \texttt{dealii::dealii}, automatically switches between
debug and release interface depending on the build type set via
\texttt{CMAKE\_BUILD\_TYPE}. The \texttt{dealii::dealii} third variant also
populates compiler and linker options, whereas for the first two variants a
client project has to ensure that the compiler and linker are properly set
up. The new import targets make it now possible to configure a dependent
project without the use of any \dealii specific macros:
%
\begin{anycode}
cmake_minimum_required(VERSION 3.13.4)
set(CMAKE_BUILD_TYPE Debug CACHE STRING "")
project(step CXX)

@@

\todo[inline]{Stefano: Anything to add here?.}

>>>>

\dealii's original CMake build system, merged for the 8.0.0 release
in 2013, was written for CMake 2.8.8 and thus lacks many of the
modern features introduced into CMake over the last several years. This
created a particular issue with an increasing number of dependencies
switching their CMake configuration to \emph{import targets}, where all
necessary information for using an external resource, such as include
directories and library link interfaces, are associated with an imported
CMake target rather than being provided with individual (and
inconsistently) named CMake variables. With the \dealii 9.5 release the
handling of external dependencies has been rewritten entirely to support
imported targets. The \trilinos and \kokkos interfaces have been
modernized. We plan to migrate all remaining dependencies to import targets
wherever possible for the next release.

\dealii's CMake project configuration itself now exports three targets,
\texttt{dealii::dealii\_debug}, \texttt{dealii::dealii\_release}, and
\texttt{dealii::dealii}. Linking against one of the first two variants via
\texttt{target\_link\_libraries()} populates the target with all necessary
include directories and the full link interface necessary for \dealii. The
third variant, \texttt{dealii::dealii}, automatically switches between
debug and release interface depending on the build type set via
\texttt{CMAKE\_BUILD\_TYPE}. The \texttt{dealii::dealii} third variant also
populates compiler and linker options, whereas for the first two variants a
client project has to ensure that the compiler and linker are properly set
up. The new import targets now make it possible to configure a dependent
project without the use of any \dealii specific macros:
%
\begin{anycode}
cmake_minimum_required(VERSION 3.13.4)
set(CMAKE_BUILD_TYPE Debug CACHE STRING "")
project(step CXX)

@@

S. Zampini was supported by the KAUST Extreme Computing Research Center.
